\iffalse

Nico Casale
Cody Orazymbetov

ECE 592 HW 4

\fi

\documentclass[]{../../ncmathy}

\begin{document}
\subsection{Comparison of methods}
The distortion value for the different wavelet-based compression methods is given in the table below 

	\begin{table}[H]
	\centering\makegapedcells
	\begin{tabular}{|| c c ||}
	\hline
	Compression Alg. & Distortion \\
	\hline
		ezw      &    25.681 \\
		spiht    &    59.991 \\
		stw      &   50.453 \\
		wdr      &    25.681 \\
		aswdr    &    25.681 \\ 
		spiht\_3d &    314.79 \\
		lvl\_mmc  &    76.358 \\ 
		gbl\_mmc\_f&    3380.8 \\ 
		gbl\_mmc\_h&    3380.8 \\
	\hline
	\end{tabular}
	\caption{Distortion values of different wavelet-based compression algorithms.}
	\end{table}

The distortion value from our kmeans implementation for $P=2$, $R = 1$ is 50.22. The 'ezw', 'wdr', and 'aswdr' give the best, \textit{i.e.} lowest distortion values; all being equal to 25.681. 

\subsection{Embedded Zerotree Wavelet (EZW) image compression}
	In the embedded zerotree wavelet image compression (EZW), the discrete wavelet transform is accomplished using hierarchical sub-bands. Sub-bands will be logarithmically spaced. They are populated by applying filters to isolate each sub-band's frequencies from the original signal. Then, an image will be decomposed into wavelets. A zerotree (data structure) is used to map the the most significant wavelets. These efficiently encode the image. Zerotrees improve the compression of the original signal. A wavelet coefficient is regarded to be insignificant when $|x| < T $, where T is some threshold. The scanning of coefficients is performed starting from the parent; the child coefficient is insignificant if parent coefficient is insignificant. Then, a sequence of thresholds will be applied to determine the significance. The coding is accomplished in an embedded way, which means that there will be a sequence of binary decisions that enable the identification of an image from the null-image. The total cost of this approach is the sum of the cost of significance map and cost of non-zero values. It has 2 advantages over kmeans. EZW can precisely control the encoding rate, and no pre-training is required. It uses a discrete wavelet transform which is also a good to capture the important features, rather than clusters that do not carry much detail. Please see the final section for our code implementation of this experiment.

\end{document}